### 2012-07-05 docs/managing_jobs/managingjobs.tex
add notes on remote visiting a movie

  \begin{itemize}
  \item From the menu, select {\em options $\rightarrow$ host profiles}
  \item Create a new host by clicking on the {\em New Host} button.
  \item Enter the {\em Host nickname} as {\tt lens}
  \item Enter the {\em Remote host name} as {\tt lens.ccs.ornl.gov}
  \item Make sure that your {\em username} is correct
  \item Check {\em Tunnel data connections through SSH}
  \end{itemize}

@@

>>>>

  \begin{itemize}
  \item From the menu, select {\em options $\rightarrow$ host profiles}
  \item Create a new host by clicking on the {\em New Host} button.
  \item Enter the {\em Host nickname} as {\tt lens}
  \item Enter the {\em Remote host name} as {\tt lens.ccs.ornl.gov}
  \item Enter the {\em Path to Visit installation} as {\tt /sw/analysis-x64/visit} (not sure if this is needed)
  \item Make sure that your {\em username} is correct
  \item Check {\em Tunnel data connections through SSH}
  \end{itemize}

@@

To make a movie (output sequence of images):
\begin{itemize}
\item save a view in \visit\ you like as a session file (File $\rightarrow$ Save session).  
\item On lens, create a file called {\tt files.visit} which lists all
  of the files you want to visualize, one per line, with {\tt /Header}
  after the filename.  This can be done simply as:
  \begin{verbatim}
  ls -1 | grep -v processed | awk '{print $1"/Header"}' > files.visit
  \end{verbatim}
  %$
  (note: the {\tt processed} bit is for when you used the script above to 
  automatically archive the data).

\item Edit the session file, searching for the name of the plotfile you
  originally visualized, and change it to read {\tt files.visit}.  Make
  sure that the path is correct.  This may appear multiple times.

\item Relaunch \visit\ locally and restore the session (File $\rightarrow$ Restore session).  It will render the first image.  Then reopen (File $\rightarrow$ ReOpen file).  After this is done, the buttons that allow you to move through the files should become active (black).

\item Resave the session file

\item To generate the frames, you have 2 options:

  \begin{enumerate}
  \item File $\rightarrow$ Save movie.  Pick {\em New simple movie},
    then set the format to {\em PNG} and add this to the output box by
    clicking the right arrow, then in the very last screen, select:
    {Later, tell me the command to run}.

   \visit\ will pop up a box showing the command to run.  Trying to
   get the currently running session of \visit\ to generate the frames
   seems problamatic.  Note: you will probably want to edit out the
   {\tt -v x.x.x} argument in the commandline to not have it force
   to use a specific version.

  \item If the session file successfully does the remote visualization
   as desired, you can run the movie via the commandline with something like:

   \begin{verbatim}
   visit -movie -format png -geometry 1080x1080 -output subchandra_cutoff3_ \
       -start 0 -end 44 -sessionfile subchandra_radvel.session
   \end{verbatim}

  \end{enumerate}

\end{itemize}
